The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-08 SC-challenge.tex
Common themes

In recognition of the general desire to improve software citation rates, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at addressing \katznote{addressing or discussing?} issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
\knnote{Anything we can say to tie these together? What didn't they do?}

>>>>

In recognition of the general desire to improve software citation rates, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at discussing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
In many cases these workshops have produced strong recommendations for their respective communities on how to best proceed.

In addition, a number of common themes arise in these workshops including 1) Highlighting the critical need for making software more ``citable'' (and therefore actions authors and publishers should take to improve the status quo) 2) Discussion of how to better measure the impact of software (and therefore attract appropriate funding) and 3) How to properly archive software (where, how and how often) and how this affects what to cite and when.
